Assessing the Impact of Rules of Origin on Trade Volumes for Least Developed Countries 

### 2024-02-15 paper/paper.qmd
Updated the figures

library(tidyverse)
library(palmerpenguins)
```

@@

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

@@

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

>>>>

##Set up packages and data files
install.packages('Hmisc')
library(tidyverse)
library(dplyr)
library(ggplot2)
library(Hmisc)

eurodata <- read_csv("../data/clean_data/cleaned_euro_data.csv")
market_share <- read_csv("../data/clean_data/market_share.csv")
```

@@

```{r}
#| label: fig-1
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

### Create Figure 1
ldc_only <-eurodata %>% group_by(year) %>% summarise(util=mean(frac), var=sd(frac))
figure1<-ggplot(data=ldc_only, aes(x=year, y=util))+
  geom_line( size=1, colour = "black")+
  geom_point(size=2, colour = "black")+
  labs(x = 'Year', y = "EBA Utilization Rate") +
  theme_bw()+
  theme(text = element_text(size=10),
        axis.text.x = element_text())
figure1

@@

Our results are summarized in @fig-1

```{r}
#| label: fig-3
#| fig-cap: "haha"
#| echo: false
#| warning: false
#| message: false

Figure3<-ggplot()+
  geom_line(data=market_share, aes(x=Year, y=share, group=type, color=type), size=1)+
  geom_point(data=market_share, aes(x=Year, y=share, group=type, color=type), size=3)+
  ylab("Market Share")+
  guides(color=guide_legend(title=""))+
  theme_bw()+theme(text = element_text(size=20))+
  scale_color_manual(values = c("Grey", "Black"))
Figure3

```{r}
#| label: fig-4
#| fig-cap: "haha"
#| echo: false
#| warning: false
#| message: false

# Filter data for bangladesh
bangladesh<-eurodata %>% filter(PARTNER_LAB=="BANGLADESH") %>%
  group_by(year, woven)%>% summarise(gsp_value=sum(gsp_value), value=sum(value))%>%
  mutate(frac=gsp_value/value)
cols <- c("1" = "black", "0" = "grey")

### Create Figure 4
figure4<-ggplot(data=bangladesh, aes(x=year, y=frac, group=as.factor(woven)))+
  geom_line(data=bangladesh, aes(x=year, y=frac, color=as.factor(woven)), size=1)+
  geom_point(data=bangladesh, aes(x=year, y=frac, color=as.factor(woven)), size=3)+
  xlab("Year")+ylab("Utilization Rate")+
  ggtitle("")+
  labs(color = "") +
  scale_color_manual(values=cols, breaks=c("1","0"),
                     labels=c("Woven", "Knit"))+theme_bw()+
  scale_x_continuous(name="Year", limits=c(2001, 2018), breaks = scales::pretty_breaks(n = 9))+
  scale_y_continuous( limits=c(.1, 1), breaks = scales::pretty_breaks(n = 5))+
  theme(legend.position="bottom", legend.direction="horizontal",
        axis.text.x = element_text(color = "black", size = 10,  face = "plain"),
        axis.text.y = element_text(color = "black", size = 10,  face = "plain"),
        axis.title.x = element_text(color = "Black", size = 10, face = "plain"),
        axis.title.y = element_text(color = "Black", size = 10, face = "plain"),
        legend.text=element_text(size=10),
        plot.title = element_text(size=10))

figure4

```{r}
#| label: fig-5
#| fig-cap: "haha"
#| echo: false
#| warning: false
#| message: false

market_share <- market_share %>%
  arrange(type, Year) %>%
  group_by(type) %>%
  mutate(yearly_growth_rate = (share - lag(share)) / lag(share) * 100)

Figure5 <- ggplot(market_share, aes(x = Year, y = yearly_growth_rate, group = type, fill = type)) + 
  geom_bar(stat = 'identity', size = 1, position = position_dodge(width = 0.9)) +
  labs(y = "Yearly Growth Rate", title = "Figure 5 Yearly Growth Rate of Market Share for China and LDCs") +
  guides(color = guide_legend(title = "")) +
  theme_bw() +
  theme(text = element_text(size = 10))

Figure5
